IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-07-26 main.tex
:pencil: Update manuscript

		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-element IRS, to a single-antenna UE over $N$ orthogonal evenly-spaced subbands. We consider the quasi-static block fading model and assume the CSIT of direct and cascaded channels are known. The signals reflected by two or more times are omitted, and the noise power is assumed too small to be harvested.

@@

			Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$\footnote{It is trivial to conclude $\bar{\rho}^{\star}=1-\rho^{\star}$ because the R-E tradeoff is maximized when no signal is wasted at the receiver.} and transform problem~\eqref{op:waveform} into a reversed GP

@@

		To evaluate the performance of the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a line parallel to the AP-UE path. Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links. $d_{\mathrm{D}}=\SI{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$ are chosen as reference. We consider a large open space Wi-Fi-like environment at center frequency \SI{5.18}{\GHz}, where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the reference path loss is \SI{-35}{\dB} at \SI{1}{\meter}. Denote $\Lambda_{\mathrm{D}},\Lambda_{\mathrm{I}},\Lambda_{\mathrm{R}}$ as the path loss of direct, incident and reflected links. All channels are assumed NLoS with taps modelled as i.i.d. CSCG random variables. Rectenna parameters are chosen as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$. The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=\SI{36}{\dBm}$ and the receive antenna gain is \SI{2}{\dBi}. Moreover, the scaling ratio is $\alpha=2$, the tolerance is $\epsilon=10^{-8}$, and we assume $\delta=\rho$ for simplicity. Each R-E region is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.

@@

		Fig.~\ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$. \emph{First,} it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy. It is because less power is allocated to each subband but more balanced DC terms are introduced to boost the harvested energy. On the other hand, Fig.~\ref{fi:waveform_subband} sorts the modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for WPT in descending order. It demonstrated that a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$. This observation origins from the rectifier nonlinearity. Although both waveforms have equivalent second-order DC terms \eqref{eq:y_I2} and \eqref{eq:y_P2}, for the fourth-order terms \eqref{eq:y_I4} and \eqref{eq:y_P4}, the modulated waveform has $N^2$ monomials with a modulation gain of \num{2} while the multisine has $(2N^3+N)/3$ monomials. Hence, the benefit of multisine outstands for a sufficiently large $N$. \emph{Second,} the R-E region is convex for $N=2,4$ and concave-convex for $N=8,16$. This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$. When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle SWIPT point obtained by PS (as the red curve in Fig.~\ref{fi:re_subband}). Compared with the linear harvester model that requires no dedicated power waveform and always prefers PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depend on the number of subbands.

@@

		\begin{figure}[!t]
			\centering
			\subfloat[Imperfect cascaded CSIT\label{fi:re_csi}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_csi.tex}
				}
			}
			\subfloat[Quantized IRS\label{fi:re_quantization}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_quantization.tex}
				}
			}
			\caption{Average R-E region with imperfect cascaded CSIT and quantized IRS for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
		\end{figure}

>>>>

		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where an $M$-antenna AP delivers information and power simultaneously, through an $L$-element IRS, to a single-antenna UE over $N$ orthogonal evenly-spaced subbands. We consider the quasi-static block fading model and assume the CSIT of direct and cascaded channels is known. The signals reflected by two or more times are omitted, and the noise power is assumed too small to be harvested.

@@

			Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$\footnote{It can be concluded $\bar{\rho}^{\star}=1-\rho^{\star}$ because the R-E tradeoff is maximized when no signal component is wasted at the receiver.} and transform problem~\eqref{op:waveform} into a reversed GP

@@

		To evaluate the performance of the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a line parallel to the AP-UE path. Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links. $d_{\mathrm{D}}=\SI{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$ are chosen as reference. We consider a large open space Wi-Fi-like environment at \SI{2.4}{\GHz} center frequency with \SI{40}{\dB} free-space path loss at \SI{1}{\meter}. The path loss of direct, incident and reflected links are denoted by $\Lambda_{\mathrm{D}}$, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$, respectively. All channels are assumed Non-Line-of-Sight (NLoS) where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the taps are modeled as i.i.d. CSCG random variables. Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$. We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{36}{\dBm}$, the receive antenna gain as \SI{2}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity. Each R-E region is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.

@@

		Fig.~\ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$. \emph{First,} it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy. It is because less power is allocated to each subband but more balanced DC terms are introduced to boost the harvested energy. On the other hand, Fig.~\ref{fi:waveform_subband} sorts the modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for WPT in descending order. It demonstrates that a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$. This observation origins from the rectifier nonlinearity. Although both waveforms have equivalent second-order DC terms \eqref{eq:y_I2} and \eqref{eq:y_P2}, for the fourth-order terms \eqref{eq:y_I4} and \eqref{eq:y_P4}, the modulated waveform has $N^2$ monomials with a modulation gain of \num{2} while the multisine has $(2N^3+N)/3$ monomials. Hence, the benefit of multisine outstands for a sufficiently large $N$. \emph{Second,} the R-E region is convex for $N \in \{2,4\}$ and concave-convex for $N \in \{8,16\}$. This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$. When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle SWIPT point obtained by PS (as the red curve in Fig.~\ref{fi:re_subband}). Compared with the linear harvester model that requires no dedicated power waveform and always prefers PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depend on the number of subbands.

@@

		\begin{figure}[!t]
			\centering
			\subfloat[Imperfect cascaded CSIT\label{fi:re_csi}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_csi.tex}
				}
			}
			\subfloat[Quantized IRS\label{fi:re_quantization}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_quantization.tex}
				}
			}
			\caption{Average R-E region with imperfect cascaded CSIT and quantized IRS for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$. $\epsilon_n^2 \to \infty$ corresponds to no CSIT and random IRS; $b=0$ and $b \to \infty$ correspond respectively to no IRS and unquantized IRS.}
		\end{figure}
